|

### 2016-01-12 manuscript/thesis_pve.Rmd
spelling

\
With high rates of g~s~, non-limiting leaf water potential ($\Psi$~pd~) and consistent leaf $\delta$^13^C across soil volume treatments there was little evidence that water stress caused the reduction in *A~n~*. This finding is consistent with other container size studies without drought treatments.  For example, reduced A~max~ in cotton seedlings grown at elevated CO~2~ was attributed to sink-limited feedback inhibition from inadequate rooting volume, not decreased g~s~ [@thomas1991root]. Additionally, severe reductions in *A~n~* in coffee plants were not attributed to impacts of container size on leaf water potentials or g~s~ [@ronchi2006growth]. It is likely that reductions in *A~n~* of well-watered seedlings observed in our study of *E.tereticornis* seedlings was instead the result of limiting soil nutrients or space restriction on belowground sink strength.

>>>>

\
With high rates of g~s~, non-limiting leaf water potential ($\Psi$~pd~) and consistent leaf $\delta$^13^C across soil volume treatments there was little evidence that water stress caused the reduction in *A~n~*. This finding is consistent with other container size studies without drought treatments.  For example, reduced A~max~ in cotton seedlings grown at elevated CO~2~ was attributed to sink-limited feedback inhibition from inadequate rooting volume, not decreased g~s~ [@thomas1991root]. Additionally, severe reductions in *A~n~* in coffee plants were not attributed to impacts of container size on leaf water potentials or g~s~ [@ronchi2006growth]. It is likely that reductions in *A~n~* of well-watered seedlings observed in our study of *E. tereticornis* seedlings was instead the result of limiting soil nutrients or space restriction on belowground sink strength.
